Hypertension and microbiome

### 2019-01-23 articletwo.Rmd
Figure 4

```{r Main contributors of PC3}
pca.rotation.abs <- abs(pca.prcomp$rotation)
pca.loading <- sweep(pca.rotation.abs, 2, colSums(pca.rotation.abs), "/") %>%
    as.data.frame %>%
    tibble::rownames_to_column(var = "term")

pca.prcomp$rotation %>% length

pca.loading %>% pull(PC3) %>% sum

pca.pc3 <- pca.loading %>%
    select(term, PC3) %>%
    arrange(-PC3) %>%
    head(20)

pca.pc3.gg <- ggplot(data=pca.pc3, aes(x=reorder(term, -PC3), y=PC3)) +
    geom_bar(stat="identity") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggsave(file = "cache/pca.pc3.png", plot = pca.pc3.gg, height = 3, width = 7, dpi = 300)
```

```{r Write figure 4}
fig4head <- ""
fig4foot <- ""
writeimage(doc, 4, "cache/pca.pc3.png", fig4head, fig4foot)
```

>>>>

```{r Main contributors of PC3}
pca.loading <- pca.prcomp$rotation^2 %>%
    as.data.frame %>%
    tibble::rownames_to_column(var = "term") %>%
    mutate(name = rename.genus(term))

pca.loading.pc3.top20 <- pca.loading %>%
    select(name, PC3) %>%
    arrange(-PC3) %>%
    head(20)

pca.pc3.gg <- ggplot(data=pca.loading.pc3.top20, aes(x=reorder(name, -PC3), y=100*PC3)) +
    geom_bar(stat="identity", width=0.5, position = position_dodge(preserve = "single")) +
    theme_classic(20) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1)) +
    xlab("") +
    ylab("Contribution (%)") +
#    coord_fixed(ratio = 1) +
    theme(axis.title.x=element_blank(),
          text = element_text(size=20),
          legend.justification=c(1,0),
          legend.position=c(1.03, 0.75),
          legend.title=element_text(size = 20),
          legend.direction="vertical",
          legend.text=element_text(size = floor(0.75*20)),
          legend.box.margin = margin(1, 1, 1, 1, "mm"),
          legend.box.background = element_rect(colour = "black"),
          aspect.ratio = 0.7)
   ggsave(file = "cache/pca.pc3.png", plot = pca.pc3.gg, height = 8, width = 8, dpi = 300) 
```

```{r Write figure 4}
fig4head <- "Bacteria causing dysentery and diarrhea contribute to third principal component"
fig4foot <- sprintf("Top 20 bacterial contributors to third principal coordinate at species level. Centered log ratio transform is performed for the compositional data. Third principal component explain %.1f%% of the total variation. Plasmid DNA is denoted using star.", pca.percentage[3])
writeimage(doc, 4, "cache/pca.pc3.png", fig4head, fig4foot)
```
